---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# familytreemakeR

<!-- badges: start -->

[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/familytreemakeR)](https://CRAN.R-project.org/package=familytreemakeR)
<!-- badges: end -->

The goal of familytreemakeR is to make it easy for a useR to listen to someome monologue about the structure of a family and, in real-time, write a pipe-based script that, when run, generates an `igraph` representing the family.

## Installation

You can install the development version of familytreemakeR from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("rcorty/familytreemakeR")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(familytreemakeR)

there_was(first_name = 'Anakin', last_name = 'Skywalker') %>% 
	who_had_a(what = 'child', first_name = 'Luke', last_name = 'Skywalker') %>% 
	who_had_a(what = 'sibling', first_name = 'Leia', last_name = 'Skywalker') %>% 
	who_had_a(what = 'child', first_name = 'Ben', last_name = 'Solo') %>% 
	print() ->
	family_tree
```

There is no special plotting function (yet), so we simply have:

```{r pressure, echo = FALSE}
plot(family_tree)
```

There are many TODO's...
